Ultra-deep $K_s$-band Imaging of the \textit{Hubble} Frontier Fields

### 2015-02-21 Paper0/ms.tex
add number counts

K-band surveys:  ISAAC, NMBS, UltraVISTA, ...

HUGS

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   Exposure Map figure
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\plotone{hawkiff_layout.pdf} % Figures/exposure_map.pdf
\caption{Layout of the Frontier Fields $K_s$-band mosaics.  The positions of the \textit{HST} cluster and parallel fields are shown in the blue (ACS optical) and red (WFC3 IR) polygons.  The area covered by the \textit{Spitzer}/IRAC 3.6 and 4.5\,\mum\ channels is shown in orange.  The bottom panels show the exposure maps, where the four HAWK-I chips and two MOSFIRE pointings can be seen.\label{fig:layout}}  
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   Exposure Map figure
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The product of the inverse curves of growth shown in Fig.~\ref{fig:cog} (i.e., aperture corrections) and the noise curves in the top panel of Fig.~\ref{fig:depth} defines an optimal photometric aperture size where this product is minimized \citep{whitaker:nmbs}.  For our $K_s$-band mosaics, this optimal aperture has $D\sim0\farcs5$, just larger than the FWHM of point-source profiles.  The $5\,\sigma$ limiting magnitudes (AB) within $0\farcs5$ diameter apertures are 25.8, 25.9, and 25.0 in the Abell 2744, MACS-0416, and MACS-0717 fields, respectively.  We note that the depths of the FF HAWK-I mosaics are nearly identical to those of the two deepest HUGS pointings in the GOODS-South Field (i.e., GOODS-South ``D1'' and ``D2'').  The image depths reported by \cite{hugs} assume ideal noise properties that can be compared to the dashed curves in Fig.~\ref{fig:depth}.  We have analyzed the HUGS GOODS-South ``D2'' image with the same empty-aperture technique as was done for the FF images, and the sensitivities are fully consistent with those reported by \cite{hugs} when accounting for the different definitions.  Along with the two HUGS deep HAWK-I fields, our images covering the Frontier Fields represent the deepest $K_s$-band images ever obtained and will provide a crucial complement to the deep \textit{HST} and \textit{Spitzer} imaging of the same fields.

@@

>>>>

K-band surveys:  ISAAC \citep{labbe:03}, NMBS, UltraVISTA, ...

Subaru Super Deep Field (AO) \cite{minowa:05}.

HUGS \citep{hugs}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   Exposure Map figure
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\plotone{hawkiff_layout.pdf} % Figures/exposure_map.pdf
\caption{Layout of the Frontier Fields $K_s$-band mosaics.  The positions of the \textit{HST} cluster and parallel fields are shown in the blue (ACS optical) and red (WFC3 IR) polygons.  The light blue polygons in the MACS-0717 field show additional wide-field ACS imaging coverage from  programs GO-9722 and GO-10420 \citep[PI: Ebeling;][]{ma:11}.  The area covered by deep imaging in the \textit{Spitzer}/IRAC 3.6 and 4.5\,\mum\ channels is shown in orange.  The bottom panels show the mosaic weight maps, where the four HAWK-I chips and two MOSFIRE pointings can be seen.\label{fig:layout}}  
\end{figure*}

@@

The product of the inverse curves of growth shown in Fig.~\ref{fig:cog} (i.e., aperture corrections) and the noise curves in the top panel of Fig.~\ref{fig:depth} defines an optimal photometric aperture size where this product is minimized \citep{whitaker:nmbs}.  For our $K_s$-band mosaics, this optimal aperture has $D\sim0\farcs5$, just larger than the FWHM of point-source profiles.  The $5\,\sigma$ limiting magnitudes (AB) within $0\farcs5$ diameter apertures are 25.8, 25.9, and 25.0 in the Abell 2744, MACS-0416, and MACS-0717 fields, respectively.  We note that the depths of the FF HAWK-I mosaics are nearly identical to those of the two deepest HUGS pointings in the GOODS-South Field (i.e., GOODS-South ``D1'' and ``D2'').  The image depths reported by \cite{hugs} assume ideal noise properties that can be compared to the dashed curves in Fig.~\ref{fig:depth}.  We have analyzed the HUGS GOODS-South ``D2'' image with the same empty-aperture technique as was done for the FF images, and the sensitivities are fully consistent with those reported by \cite{hugs} when accounting for the different definitions.  The HAWK-I images presented here are among the deepest $K_s$-band images ever obtained and will provide a crucial complement to the deep \textit{HST} and \textit{Spitzer} imaging of the Frontier Fields.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Number counts figure
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\epsscale{1.18}
\plotone{number_counts_all.pdf} % Figures/exposure_map.pdf
\caption{Number counts.\label{fig:counts}}  
\end{figure*}
